Bad forecast, good decision: predictive accuracy is not everything

### 2021-01-01 manuscript/manuscript.Rmd

---
title: 'Bad forecast, good decision: predictive accuracy is not everything'
author:
- name: Carl Boettiger
  email: cboettig@berkeley.edu
  affiliation: ucb,corr
date: "`r Sys.Date()`"
output: rticles::pnas_article
abstract: |
  Model-based forecasts have been enabled by recent explosion of data and computational methods and spurred on by decision-makers appetite for forecasts in everything from elections to pandemic response. It is taken for granted that the model which makes the most accurate forecast, accounting for uncertainty, will also be the best model to inform decision-making.  Using a classic example from fisheries management, I demonstrate that selecting the model that produces the best forecast can lead to decidedly worse outcomes. This situation can arise whenever the models are only approximations of the reality, underscoring the risk of evaluating models only by prediction accuracy and not decision objectives using formal tools of decision theory.

corresponding_author:
  code: corr
  text: "To whom correspondence should be addressed. E-mail: cboettig@berkeley.edu"

bibliography: refs.bib
address:
- code: ucb
  address: ESPM Department, University of California, 130 Mulford Hall Berkeley, CA
    94720-3114, USA

@@

significance: |
  ...

@@

keywords:
  - one
  - two
  - optional
  - optional
  - optional

@@

output: rticles::pnas_article

---

>>>>

---
title: 'Bad forecast, good decision: predictive accuracy is not everything'
author:
- name: Carl Boettiger
  email: cboettig@berkeley.edu
  affiliation: a,1
date: "`r Sys.Date()`"

abstract: |
  Model-based forecasts have been enabled by recent explosion of data and computational methods and spurred on by decision-makers appetite for forecasts in everything from elections to pandemic response. It is taken for granted that the model which makes the most accurate forecast, accounting for uncertainty, will also be the best model to inform decision-making.  Using a classic example from fisheries management, I demonstrate that selecting the model that produces the most accurate and precise forecast can lead to decidedly worse outcomes. This situation can arise whenever the models are only approximations of the reality, underscoring the risk of evaluating models only by prediction accuracy and not decision objectives using formal tools of decision theory.

corresponding_author:
  code: 1
  text: "To whom correspondence should be addressed. E-mail: cboettig@berkeley.edu"

bibliography: refs.bib
address:
- code: a
  address: Department of Environmental Science, Policy, and Management, University of California, 130 Mulford Hall Berkeley, CA
    94720-3114, USA

@@

significance: |
  It is natural to assume that a more accurate and precise forecast will lead to better decisions
  than a less accurate one.  I demonstrate that this premise is false, and illustrate how a 
  decision-theoretic approach provides better criteria for chosing a forecast model than forecast skill.
  As the expansion of machine learning methods and big data lead to increasing more accurate and
  precise forecasts in many fields, we should remember that alone is not enough to jettison earlier 
  models.

@@

@@

output: rticles::pnas_article
---
